---
title: "Adam_Ageeb_HW_8"
author: "Adam Ageeb"
date: "2025-04-09"
output: html_document
---

# Adam Ageeb
## UT EID ara4629
### GitHub Link: 

### Problem 1

#### Part A
```{r, echo = FALSE, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(ggplot2)
library(mosaic)
creatinine <- read_csv("/Users/adamageeb/Documents/SDS 315/HW8/creatinine.csv")
reg_creatinine <- lm(creatclear ~ age, data = creatinine)
summary(reg_creatinine)
plot(creatinine$age, creatinine$creatclear)
```

I used the lm() function in base R to find the regression line equation of "expected_creatinine_clearance = -0.61982*age + 147.81292. I plugged in 55 for age to find the expected creatinine clearance for a 55-year-old to be an about 113.72 mL/minute.

#### Part B
```{r, echo = FALSE, message=FALSE, warning=FALSE}

```

Based on the regression line creatinine clearance decreases by 0.61982 mL/minute for every additional year of life. This is the slope of the regression line equation.

#### Part C
```{r, echo = FALSE, message=FALSE, warning=FALSE}
135 - (40*(-0.61982) + 147.81292)
112 - (60*(-0.61982) + 147.81292)
```

I'll determine this by finding which person has the best creatinine clearance in comparison to what they're expected to be have. The 40-year-old has a creatinine clearance 11.98 mL/minute higher than excepted compared to the 60-year-old who only exceeded expectations by 1.38 mL/minute. The 40-year-old is healthier for their age.


### Problem 2

```{r, echo = FALSE, message=FALSE, warning=FALSE}
covid <- read_csv("/Users/adamageeb/Documents/SDS 315/HW8/covid.csv")
covid_Italy <- covid |>
  filter(country == "Italy") |>
  mutate(log_deaths = log(deaths))
boot_Italy <- do(10000) * {
  model <- lm(log_deaths ~ days_since_first_death, data = resample(covid_Italy))
  coef(model)[2]
}
boot_Italy <- boot_Italy |>
  mutate(doubling_time = (log(2)/days_since_first_death))
quantile(boot_Italy$days_since_first_death, probs = c(0.025, 0.975))
quantile(boot_Italy$doubling_time, probs = c(0.025, 0.975))

covid_Spain <- covid |>
  filter(country == "Spain") |>
  mutate(log_deaths = log(deaths))
boot_Spain <- do(10000) * {
  model <- lm(log_deaths ~ days_since_first_death, data = resample(covid_Spain))
  coef(model)[2]
}
boot_Spain <- boot_Spain |>
  mutate(doubling_time = (log(2)/days_since_first_death))
quantile(boot_Spain$days_since_first_death, probs = c(0.025, 0.975))
quantile(boot_Spain$doubling_time, probs = c(0.025, 0.975))

ggplot(covid, aes(x = days_since_first_death, y = deaths, color = country)) +
  geom_line(size = 1) +
  labs(
    title = "Reported Daily COVID-19 Deaths Over Time",
    x = "Days Since First Death",
    y = "Daily Deaths",
    color = "Country"
  )
```

I went about this by first taking the log() of deaths to create the log_deaths variable for each country separately. I did this because these are exposition growth models and by taking the log I can find the slope of the regression line comparing the new data and that slope will be the exponential growth rate of the initial deaths variable. Next, I bootstrapped the the data and found the slope each time. Finally, I found the 95% confidence intervals for the slopes of each country, which are actually the exponential growth rates. Using the bootstrapped data I made a new variable called doubling_time using the eqation "log(2)/r" and found the 95% confidence interval of that.

1. I am 95% confident that the estimated exponential growth rate for Covid deaths in Italy is between 0.159 and 0.208. I am 95% confident that the estimated doubling time for Covid deaths in Italy is between 3.3 and 4.4 days.

2. I am 95% confident that the estimated exponential growth rate for Covid deaths in Spain is between 0.235 and 0.318. I am 95% confident that the estimated doubling time for Covid deaths in Italy is between 2.2 and 2.9 days.

3. Graph above.

### Problem 3

```{r, echo = FALSE, message=FALSE, warning=FALSE}
milk <- read_csv("/Users/adamageeb/Documents/SDS 315/HW8/milk.csv")
milk <- milk |>
  mutate(log_price = log(price), log_sales = log(sales))
boot_milk <- do(10000) * {
  model <- lm(log_sales ~ log_price, data = resample(milk))
  coef(model)[2]
}
confint(boot_milk, level = 0.95)
```

I estimated the price elasticity of demand for milk by taking the log of the equation, "log(sales)=α+βlog(price)". The slope β represents the price elasticity. I bootstrapped the data set 10,000 times and extracted the slope each time. The average elasticity was -1.618578, and the 95% confidence interval ranged from -1.772579 to -1.449724.